Commit Rater

### 2015-08-24 presentations/paper/methodology.tex
Add stubs for criteria descriptions

>>>>

Each commit of an author has been testet against the following criteria. While most tests either \emph{fail} or \emph{pass}, some criteria may not be appliccable in some situations, e.g. a commit message's body cannot be tested for a per-line character limit, if there is no body at all. In those cases, the criterion-test will count as \emph{undefined}.

\subsubsection{subject_limit}
\label{subs:subject_limit}

\subsubsection{capitalize_subject}
\label{subs:capitalize_subject}

\subsubsection{no_period_subject}
\label{subs:no_period_subject}

\subsubsection{imperative_subject}
\label{subs:imperative_subject}

\subsubsection{body_used}
\label{subs:body_used}

\subsubsection{body_limit}
\label{subs:body_limit}

\subsubsection{empty_second_line}
\label{subs:empty_second_line}

\subsubsection{no_short_message}
\label{subs:no_short_message}

\subsubsection{no_long_message}
\label{subs:no_long_message}

\subsubsection{no_bulk_change}
\label{subs:no_bulk_change}

\subsubsection{no_vulgarity}
\label{subs:no_vulgarity}

\subsubsection{no_misspelling}
\label{subs:no_misspelling}

\subsubsection{no_duplicate}
\label{subs:no_duplicate}
